---
title: "Exploration"
author: "Grace Lawley"
date: "8/13/2019"
output: 
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE, warning = FALSE}
library(readr)
library(dplyr)
library(purrr)
library(stringr)
library(knitr)
library(tidyr)
```


# Jenny's 2016 syllabus

```{r}
syllabus_raw <- read_csv("../course-admin/class-meetings/class-meetings.csv")

syllabus_raw %>% 
  kable()
```

# Adapting Jenny's 2016 syllabus for the STAT545 reboot

## Some restructuring 

* Mapping *STAT545A* and *STAT547M* to Part I and Part II
* Mapping each pair of cm's to Week 1, Week 2,..., Week 13
* Mapping *tues* to *thurs* to A and B (so Week 1A, Week 1B, etc.)


```{r}
syllabus <- syllabus_raw %>% 
  mutate(part = case_when(course == "STAT545A" ~ "I", course == "STAT547M" ~ "II"),
         section = case_when(dow == "tues" ~ "A", dow == "thurs" ~ "B"), 
         week = rep(seq(1, 13), each = 2),
         week = str_c(week, section)) %>% 
  select(part, week, raw_notes, cm) %>% 
  rename(cm_notes = raw_notes)
```

## Gathering the class meeting (cm) file paths

```{r}
cm_df <- 
  tibble(cm_file = list.files(path = "../", pattern = "^cm.*\\.md")) %>% 
  mutate(cm = str_extract(cm_file, "cm[:digit:]{3}")) 

cm_df %>% 
  kable()
```


## Adding the cm file paths to the syllabus

```{r}
syllabus <- syllabus %>% 
  left_join(cm_df, by = "cm") %>% 
  select(part, week, cm, cm_notes, cm_file)

syllabus %>% 
  kable()
```


# Homework Files

I haven't found a table linking each homework to a specific class meeting. The homeworks appear to be assigned within the class meetings. I do know that homework 01-05 were for STAT545A and homework 06-10 were for STAT547M.

```{r}
hw_df <- 
  tibble(file = list.files(path = "../", pattern = "^hw.*\\.md")) %>% 
  mutate(hw = str_extract(file, "hw[:digit:]{2}")) %>% 
  group_by(hw) %>% 
  nest(.key = "hw_file")

hw_df %>% 
  kable()
```


## Proposal for where to assign the homeworks 

*These will likely change when I do a close look at each of the assignments and class meetings*

```{r}
hw_dates <- hw_df %>% 
  # raw_notes are pulled from Jenny's syllabus
  mutate(hw_notes = c("General Homework Guidelines", 
                   "Edit README.md and Use R Markdown",
                   "Explore Gapminder and use dplyr",
                   "Manipulate, summarize, visualize Gapminder with dplyr and ggplot2",
                   "Tidy data and joins",
                   "Factor and figure management; Repo hygiene",
                   "Data wrangling conclusion",
                   "Automate a data analysis pipeline",
                   "Build a Shiny app",
                   "Write an R package",
                   "Get data from the web"),
         cm = c("cm001", "cm004", "cm006", "cm008", "cm010", "cm014",
                "cm104", "cm106", "cm108", "cm110", "cm112"))


hw_dates %>% 
  kable()
```


```{r}
syllabus %>% 
  left_join(hw_dates, by = "cm") %>% 
  select(part, week, cm, cm_notes, hw, hw_notes, cm_file, hw_file) %>% 
  kable()

```




